### 2017-02-20 Hhh/Hhh.tex
Hhh edit

\chapter{\texorpdfstring{Search for \Htohhtobbtautau}{Search for H -> hh -> bbtautau}}
\label{chap:hhh}
In this chapter the search for a heavy Higgs boson decaying to a pair of 125 GeV Higgs bosons, with one of these Higgs bosons decaying to 
a pair of b-jets and the other decaying to a pair of \Ptau leptons is discussed. In this analysis, which 
uses a dataset corresponding to 19.8 fb$^{-1}$ collected during the 2012 p--p running
period of the \ac{LHC}, the \etau, \mutau and \tautau final states
of the \Pgt-pair are studied; these final states are referred to as channels. 
The results of this search are model-independent
upper limits on the heavy Higgs production cross--section times branching ratio into h(125)h(125)$\rightarrow b\bar{b} \tau\tau$, for
which all three channels are combined. The \etau and \mutau channels will be described in this chapter, the \tautau channel will not
be covered, although the limits shown in section \ref{sec:hhh_results} will include this final state.
In addition  the results are interpreted in the context of the MSSM and a type-II Two Higgs Doublet Model (2HDM), 
these interpretations are made in combination with the results of a search for \AtoZhtolltautau \cite{CMS-HIG-14-034}. 
My work focussed on checks for the \mutau and \etau channels, as well as being
responsible for limit setting for the \Htohh analysis, and performing the model interpretations
of the \Htohh and \AtoZh analyses, plus their combination.
Both searches, and their interpretation, are detailed in reference \cite{CMS-HIG-14-034}.

The discovery of the 125 GeV Higgs boson by the ATLAS and CMS collaborations in 2012 \cite{HDiscoveryATLAS,HDiscoveryCMS} has opened up
new possibilities for probing the Higgs sector beyond the Standard Model. As discussed in chapter \ref{chap:theory}, in some \ac{MSSM} scenarios, and some more
generic type-II 2HDM's, a heavy neutral Higgs boson H can decay to a pair of 125 GeV Higgs bosons for low values
of \tanb, probing a region of phase space not yet excluded by the stringent existing limits. In regions where
the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
of both channels for probing the low-\tanb~region. The $b\bar{b}$\tautau final state is chosen for the combination
of the large $h(125) \rightarrow b\bar{b}$ branching ratio and the cleaner \htotautau final state.

\section{Datasets and \acl{MC} samples}
\label{sec:hhh_datasets}
The dataset used for this analysis corresponds to the full dataset collected by the CMS experiment during the 2012 $p-p$ 
running period of the LHC. 
Signal and background events were generated using several different \ac{MC} event generators. The \texttt{MadGraph}
\cite{madgraph} matrix element generator was used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ ,\WZ and \WW
events. In addition to samples with a mixture of jet multiplicities (`inclusive' samples), samples binned in jet multiplicity
were used for the \Wjets and \Zellell backgrounds. This increases the number of background events
in regions with multiple jets, which are important for this analysis due to the presence of b-jets in the final state. 
The samples binned in jet multiplicity are combined with the
inclusive samples such that the fraction of events with each jet multiplicity is preserved.

Single top samples were produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of $gg\rightarrow$\Htohhtobbtautau
were generated in steps of 10 GeV between \mH $= 260 - 350$~GeV using \texttt{PYTHIA 6} \cite{pythia64}. The signal
\ac{MC} is limited to 350 GeV because for the interpretation of a resonance as a Higgs boson the decay \PHiggs $\rightarrow$ \ttbar
starts to dominate beyond this mass. In all of the samples
\texttt{TAUOLA} \cite{tauola} is used to decay $\tau$s, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
Minimum bias events generated using \texttt{PYTHIA 6} are added to all \ac{MC} samples to model additional
interactions. The \ac{MC} samples are then reweighted so that the pile--up distribtuion matches the
pile--up distribution in data.

To better model the \Ztautau background, an embedding technique is used. In this method, 
\Zmm events are selected in data and the muons are replaced by generator-level taus. \texttt{TAUOLA} is used
to decay the taus and tau polarisation effects are modelled using \texttt{TauSpinner} \cite{TauSpinner}. The detector
response to the tau decay products is modelled using the \texttt{GEANT4}-based \cite{Geant4} detector simulation, and 
tracks in the inner tracking system, hits in the muon systems and energy deposits in the calorimeters
due to the simulated taus are combined with the remains of the \Zmm event after the detector signals
of the two muons originiating from the \PZ have been removed. This technique is also applied to 
a \ttbar background sample to estimate the \ttbar contamination in the embedded sample. This contribution
needs to be subtracted from the \Ztautau background estimated using the embedded \Zmm sample to
avoid double counting with the \ttbar \ac{MC}.

\section{Event selection and categorisation}
\label{sec:hhh_selection}
This section gives an overview of the event selection, a detailed description of the physics
objecs used in this analysis is given in chapter OBJECTS.

@@

In the offline event selection, an oppositely charged \mutau pair is required, 
separated by $\Delta R > 0.5$.
The muon is required to have a \pT~of at 
least 20 GeV and $|\eta| < 2.1$, and should be compatible with originating from the 
primary vertex. This means the impact parameters $d_{xy}$ and $d_{z}$ must be smaller
than 0.045 and 0.2 cm respectively. Tight muon identification
criteria and tight isolation requirements $I_{\text{rel}}^{\mu} < 0.1$, as described 
in section OBJECTS, are applied. The hadronic tau must have a \pT~of at least
20 GeV, $|\eta| < 2.3$, and must have $d_{z} < 0.2$ cm. It is required to pass 
the decay mode finding identification
from the HPS algorithm. Additionally
the raw combined isolation is required to be
at most 1.5 GeV. To reject $\Pe/\Pgm \rightarrow \Pgt_{h}$ fakes, and to
reduce the contribution of \Zmm background events, the hadronic tau is 
also required to pass the tight working point of the anti-$\Pgm$ discriminator
and the loose working point of the cut--based anti-$\Pe$ discriminator.

After this selection there is still a chance more than one possible 
\mutau pair exists
in the event. If this is the case, the combination with largest 
\pT$^{\Pgm}$ + \pT$^{\Pgt_{h}}$ is chosen. In order to reduce \Zmm 
backgrounds further, for cases where the reconstructed hadronic tau originates
from a misidentified jet, the event is rejected if an opposite--charge pair 
of lower \pT (at least 15 GeV) muons, passing looser ID and isolation requirements
than the signal muon, can be formed. Additional vetos, requiring exactly one muon and 
exactly zero electrons to pass \pT $>10$ GeV and loose ID and isolation requirements, 
are applied to reduce the \WZ background.

In addition to the requirements on the di--tau pair, at least 2 jets with \pT$ >20$ GeV are 
required. No b--tagging requirements are applied at this stage, these will be discussed 
in more detail in section \ref{sec:hhh_selection_categories}.

@@

\subsection{\texorpdfstring{Event selection in the \etau channel}{Event selection in the e-tau channel}}
\label{sec:hhh_selection_etau}
Events in the \etau channel are selected using a trigger which requires an electron at L1, and both an electron
and a hadronic tau at HLT.
The hadronic
tau is reconstructed in a similar way as for the trigger in the \mutau channel, and loose ID and isolation requirements
are also applied to the electron at this stage.

After the trigger selection, an oppositely charged \etau pair is required, again separated by $\Delta R >0.5$. 
The electron should have a \pT~of at least 24 GeV, $|\eta| < 2.1$, and should
satisfy $d_{xy} < 0.045$cm and $d_{z} < 0.2$ cm. The electron must pass the tight
working point of the electron MVA ID discriminator, and the
relative isolation is required to be $I_{rel}^{\Pe} < 0.1$. The requirements placed on the
hadronic tau are similar to those required in the \mutau channel, apart from the anti-$\Pgm$ discriminator,
where the loose working point is required, and the anti--$\Pe$ discriminator, where the medium
working point of the MVA discriminator is required.

If there is more than one possible \etau pair, The pair with largest \pT$^{\Pe}$+\pT$^{\Pgt_{h}}$
is taken. Similar additional vetos as in the \mutau channel are applied.
the event is rejected if an opposite--charge pair of electrons with \pT $> 15$ GeV, passing looser ID and
isolation requirements than the signal electron requirements, can be formed. To reduce the \WZ
background, events that have more than one electron or at least one muon passing \pT $>10$ GeV and loose ID and isolation
requirements are rejected.

In addition to the requirements on the di--tau pair, at least 2 jets with \pT $>20$ GeV are 
required.

@@

\subsection{Categorisation}
\label{sec:hhh_selection_categories}
In both channels a selection on the transverse mass, \mT,~between the electron/muon
and missing transverse energy, defined as,
\begin{equation}\label{eqn:hhh_selection_mt}
m_{\text{T}} = \sqrt{2p_{\text{T}}E_{\text{T}}^{\text{miss}}(1-\cos{\Delta\phi})},
\end{equation}
is applied.
In this eqation \pT~is the transverse momentum of the electron or muon, and $\Delta\phi$ the azimuthal
angle between the light lepton and the missing transverse energy. The \mT~distributions for the \etau
and \mutau channels, using the selections as
described in sections \ref{sec:hhh_selection_mutau} and \ref{sec:hhh_selection_etau},
are shown in figure \ref{fig:Hhh_selection_mt}.

\begin{figure}[h!]
\begin{center}
\subfloat[\mutau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mt_1_2jetinclusive_mt_2012.pdf}}
\subfloat[\etau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mt_1_2jetinclusive_et_2012.pdf}}
\end{center}
\caption{\mT~distributions in the \mutau (left) and \etau (right) channels}
\label{fig:Hhh_selection_mt}
\end{figure}

This quantity is required to be smaller than 30 GeV in both channels. In events
where the missing energy and the light lepton are oriented back--to--back, \mT~is
large, whereas it is closer to zero when the two are aligned. In $\PW\rightarrow\ell\nu$
events, as the W is very heavy, the lepton and neutrino are more likely to be emitted back--to--back,
therefore \mT~will be large. For \Ztautau and \htotautau events, in a $\tau\rightarrow\ell\nu\nu$ decay 
the neutrinos are more likely to travel in the same direction as the visible decay products of 
the tau, due to the smaller mass of the \Pgt compared with the \PW. Therefore requiring the
transverse mass to be less than 30 GeV reduces the \Wjets background. This effect
is also visible in figure \ref{fig:Hhh_selection_mt}, where the \Wjets and the much
smaller diboson and single-top backgrounds are combined into the `electroweak' background contribution, drawn in red.
%In this analysis the presence of at least 2 jets increases the relative fraction of \ttbar 
%background events. Because the missing energy can now originate from multiple
%heavy objects (two tops) the missing transverse energy alignment is randomised. In some
%cases the lepton and missing transverse energy can be very much like the W decay
%topology, whereas in other cases \mT will be lower

After applying the \mT~selection, events are divided into three categories to maximise
sensitivity to the signal: 2jet-0tag (at least 2 jets, exactly 0 of which are b-tagged), 2jet-1tag 
(at least 2 jets, exactly 1 of which is b-tagged), 2jet-2tag (at least 2 jets, at least 2 of which are b-tagged).
Jets are considered b-tagged if they pass the medium working point of the \ac{CSV} b-tagging discriminator.
The 2jet-0tag category does not collect much of the signal and is dominated by 
backgrounds, the 2jet-2tag category is the most sensitive to signal. 
Figure \ref{fig:Hhh_selection_bjets}, which shows the number of b-tagged jets in the 2-jet selection of the \mutau and \etau
channels, illustrates this.

\begin{figure}[h!]
\begin{center}
\subfloat[\mutau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/n_bjets_csv_2jetinclusive_mt_2012_log.pdf}}
\subfloat[\etau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/n_bjets_csv_2jetinclusive_et_2012_log.pdf}}
\end{center}
\caption{Number of b-tagged jets in the 2-jet selection of the \mutau (left) and \etau (right) channels. The signal
at \mH~=$300$~GeV and \tanb~=2, multiplied by a factor of 10, is overlaid on the figures.}
\label{fig:Hhh_selection_bjets}
\end{figure}

In signal events, the di--tau pair and di--jet pair 
are the decay products of a 125 GeV Higgs boson, therefore their invariant
masses should be close to 125 GeV. To reduce background contributions
from events where the di--tau or di--jet mass is not compatible with
125 GeV, requirements are made on the di--jet invariant mass and the di--tau
invariant mass as reconstructed using the \texttt{SVFit} algorithm \cite{HDiscoveryCMS,SVFit}. This algorithm provides
a likelihood-based estimate of the di-tau mass using the visible decay products
of the taus and the reconstructed \MET. The use of this algorithm greatly
improves the separation between $Z\rightarrow\Pgt\Pgt$ and $H\rightarrow\Pgt\Pgt$ events, 
which is of great importance for the SM $H\rightarrow\Pgt\Pgt$ analysis \cite{HDiscoveryCMS}.
By requiring $70 < m_{jj} < 150$ GeV and $90 < m_{\Pgt\Pgt} < 150$ GeV a 
large number of background events can be rejected, while retaining
most of the signal. This is illustrated in figure \ref{fig:Hhh_selection_masscuts} for 
the 2jet-2tag category.

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\Pgt\Pgt}$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/m_sv_2jet2tag_mt_2012.pdf}}
\subfloat[$m_{jj}$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mjj_2jet2tag_mt_2012.pdf}}
\end{center}
\caption{Reconstructed di-\Pgt invariant mass (left) and di-jet invariant mass (right) in the 2jet-2tag category of the \mutau
channel. The signal for a heavy Higgs boson H with mass \mH = 300 GeV at \tanb=2 in the low \tanb~ MSSM scenario, enlarged by a factor 10, is overlaid on the figures.
In both variables the signal peaks at around 125 GeV.}
\label{fig:Hhh_selection_masscuts}
\end{figure}

\section{\acl{MC} to data correction factors}
\label{sec:hhh_datamc}
\ac{MC} samples are used for the estimation of some of the backgrounds and the signal, 
and it is therefore important to correct for any mismodelling. The \ac{MC} to data 
correction factors used for this are estimated in dedicated control regions.

Data and \ac{MC} identification, isolation, and trigger efficiencies
are measured for electrons, muons and hadronic taus. The difference between
the efficiencies in data and \ac{MC} are applied to \ac{MC} events as a
scale factor $SF = \frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.

For electrons and muons, these efficiencies are measured using a 
tag--and--probe method using \Zeenog and \Zmmnog events, respectively.
The hadronic tau identification, isolation and trigger efficiencies
are measured via a similar method that makes use of
$Z\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgt_{h}$ events.

The energy scale for hadronic taus is determined by fitting the mass of the 
hadronic tau candidate in $Z\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgt_{h}$ events.
This fit is performed separately for each hadronic tau decay mode to obtain
an energy scaling that is applied to reconstructed hadronic taus matched
to generator-level hadronic tau decays in MC events.

In the \etau channel a \ac{MC} to data scale factor is applied
to the \Zee background, to correct for differences in the $e\rightarrow\Pgt_{h}$
fake rate between data and \ac{MC}. This scale factor is derived separately
for the 1-prong + 0$\pi^0$ hadronic tau decay mode, and 1-prong + at least one
$\pi^0$ decay modes by fitting the visible mass of the \Pe+$\Pgt_{h}$ pair
in events passing the selection of the \etau channel as described in section
\ref{sec:hhh_selection_etau}, with the 2-jet requirement lifted.

Differences in \MET resolution and response between data and \ac{MC} are accounted for by
applying Z--recoil corrections to DY, \Wjets and signal \ac{MC} events. Chapter OBJECTS
gives more details on how these corrections are derived.

To correct for the difference in b--tagging efficiency and light jet mis--tagging
rates between data and \ac{MC} \pT~and $\eta$~dependent scale factors are 
derived using the method described in ref. \cite{BTV8TeV}. There are separate scale factors for 
b-/c- jets and light jets. Multiple possible ways to apply these scale factors
exist, for this analysis this is done through a promote/demote method.

In this method a demotion or promotion probability is assigned to every
jet as:
\begin{align}\label{eqn:promotedemote}
&P(\text{demote}) = 1 - SF \text{  for SF < 1 }  \notag \\
&P(\text{promote}) = \frac{(SF - 1)(\epsilon_{\text{MC}}-1)}{SF} \text{    for SF > 1},
\end{align}
Where $SF$ is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
the b--tagging efficiency in \ac{MC} events for the type of jet (light, b- or c-)
under consideration.

\section{Discriminating variable}
\label{sec:hhh_discr}
The variable of interest in this analysis is the mass of the heavy Higgs boson H. This can be
reconstructed as the 4--body mass of the two jets and the two taus; however
a more accurate result can be obtained by using a kinematic fitting 
procedure that makes use of the 125 GeV mass constraint on the di--tau and
di--jet candidates.

>>>>

\chapter{\texorpdfstring{Search for \Htohhtobbtautau}{Search for H -> hh -> bbtautau}}
\label{chap:hhh}
In this chapter the search for a heavy Higgs boson decaying to a pair of $125\,\GeV$ Higgs bosons, with one of these Higgs bosons decaying to 
a pair of b-jets and the other decaying to a pair of tau leptons is discussed. In this analysis, which 
uses a dataset corresponding to $19.8\,\invfb$ collected during the 2012 p-p running
period of the \ac{LHC}, the \etau, \mutau and \tautau final states
of the di-tau pair are studied; these final states are referred to as channels. 
The results of this search are model-independent
upper limits on the heavy Higgs production cross section times branching ratio (\xsbr) into h(125)h(125)$\rightarrow \Pbottom\Pbottom\Pgt\Pgt$, for
which all three channels are combined. The \etau and \mutau channels will be described in this chapter. The \tautau channel will not
be covered, although the limits shown in section \ref{sec:hhh_results} will include this final state.
In addition the results are interpreted in the context of the \ac{MSSM} and a type-II \ac{2HDM}.
These interpretations are made in combination with the results of a search for \AtoZhtolltautau \cite{CMS-HIG-14-034}. 
For these results I contributed to the analysis of the \etau and \mutau channels,
and was responsible for limit setting for the \Htohh analysis. This included performing the model interpretations
of the \Htohh and \AtoZh analyses, plus their combination.
Both searches, and their interpretations, are detailed in reference \cite{CMS-HIG-14-034}.

The discovery of the $125\,\GeV$ Higgs boson by the ATLAS and CMS Collaborations in 2012 \cite{HDiscoveryATLAS,HDiscoveryCMS} has opened up
new possibilities for probing the Higgs sector beyond the \ac{SM}. As discussed in chapter \ref{chap:theory}, in some \ac{MSSM} scenarios and some more
generic type-II \acp{2HDM}, a heavy neutral Higgs boson \PHiggs can decay to a pair of $125\,\GeV$ Higgs bosons for low values
of \tanb, probing a region of parameter space not yet excluded by the stringent existing limits. In regions where
the decay \Htohh is enhanced, the \AtoZh decay also has a large branching ratio, indicating the usefulness
of both channels for probing the low \tanb~region. The $\Pbottom\Pbottom\Pgt\Pgt$ final state is chosen for the combination
of the large $\PHiggslight(125) \rightarrow \Pbottom\Pbottom$ branching ratio and the cleaner \htotautau final state.

\section{Datasets and \acl{MC} samples}
\label{sec:hhh_datasets}
The dataset used for this analysis corresponds to the full dataset collected by the CMS experiment during the 2012 p-p 
running period of the LHC. 
Signal and background events were generated using several different \ac{MC} event generators. The \texttt{MadGraph}
\cite{madgraph} matrix element generator was used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ, \WZ and \WW
events. In addition to samples with a mixture of jet multiplicities (`inclusive' samples), samples binned in jet multiplicity
were used for the \Wjets and \Zellell backgrounds. This increases the number of background events
in regions with multiple jets, which are important for this analysis due to the presence of b-jets in the final state. 
The samples binned in jet multiplicity are combined with the
inclusive samples such that the fraction of events with each jet multiplicity is preserved.

Single top samples were produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of \ggHtohhtobbtautau
were generated in steps of $10\,\GeV$ between \mH $= 260$ -- $350\,\GeV$ using \texttt{PYTHIA 6} \cite{pythia64}. The maximum
 mass is $350\,\GeV$ because for the interpretation of a resonance as a Higgs boson the decay \PHiggs $\rightarrow$ \ttbar
starts to dominate beyond this mass. In all of the samples
\texttt{TAUOLA} \cite{tauola} is used to decay the tau leptons, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
Minimum bias events generated using \texttt{PYTHIA 6} are added to all \ac{MC} samples to model additional
interactions. The \ac{MC} samples are then reweighted so that the pileup distribution matches the
pileup distribution in data. The detector response to the final simulated particles is modelled using a \texttt{GEANT4}-based \cite{Geant4} detector simulation.

To better model the \Ztautau background an embedding technique is used. In this method, 
\Zmm events are selected in data and the muons are replaced by simulated taus. \texttt{TAUOLA} is used
to decay the taus, with the final state particles passed through the detector simulation. %and tau polarisation effects are modelled using \texttt{TauSpinner} \cite{TauSpinner}. 
Tracks in the inner tracking system, hits in the muon systems and energy deposits in the calorimeters
due to the simulated taus are combined with the remains of the \Zmm event after the detector signals
of the two muons originiating from the \PZ boson have been removed. This technique is also applied to 
a simulated \ttbar sample to estimate the \ttbar contamination in the \Zmm embedded sample. %This contribution
%needs to be subtracted from the \Ztautau background estimated using the embedded \Zmm sample to
%avoid double counting with the \ttbar \ac{MC}.

\section{Event selection and categorisation}
\label{sec:hhh_selection}
This section gives an overview of the event selection; a detailed description of the physics
objecs used in this analysis is given in chapter \ref{chap:objects}.

@@

In the offline event selection, an oppositely charged \mutau pair is required, 
separated by $\Delta R > 0.5$.
The muon is required to have a \pT~of at 
least $20\,\GeV$ and $|\eta| < 2.1$, and should be compatible with originating from the 
primary vertex. This means the transverse and longitudinal impact parameters with respect to the primary vertex, $d_{xy}$ and $d_{z}$, must be smaller
than $0.045\,\cm$ and $0.2\,\cm$ respectively. Tight muon identification
criteria and a tight isolation requirement, $I_{\text{rel}}^{\mu} < 0.1$,
 are applied. The hadronic tau must have a \pT~of at least
$20\,\GeV$, $|\eta| < 2.3$, and must have $d_{z} < 0.2\,\cm$. It is required to pass 
the decay mode finding identification
from the HPS algorithm. Additionally,
the combined isolation is required to be
at most $1.5\,\GeV$. To reject $\Pe/\Pgm \rightarrow$ \Pgth fakes, and to
reduce the contribution of \Zmm background events, the hadronic tau is 
also required to pass the tight working point of the anti-$\Pgm$ discriminator
and the loose working point of the cut-based anti-$\Pe$ discriminator.

After this selection there is still a chance that more than one possible 
\mutau pair exists
in the event. If this is the case the combination with largest 
\pT$^{\Pgm}$ + \pT$^{\Pgth}$ is chosen. In order to reduce the \Zmm 
background further, in cases where the reconstructed hadronic tau originates
from a misidentified jet, the event is rejected if an opposite-charge pair 
of lower \pT~(at least $15\,\GeV$) muons, passing looser ID and isolation requirements
than the signal muon, can be formed. Additional vetoes, requiring exactly one muon and 
exactly zero electrons to pass \pT~$>10\,\GeV$ and loose ID and isolation requirements, 
are applied to prevent overlap with other channels and to reduce the di-boson background.

In addition to the requirements on the di-tau pair, at least two jets with \pT~$>20\,\GeV$ are 
required. No b-tagging requirements are applied at this stage, these will be discussed 
in more detail in section \ref{sec:hhh_selection_categories}.

@@

\subsection{\texorpdfstring{Event selection in the \etau channel}{Event selection in the e-tau channel}}
\label{sec:hhh_selection_etau}
Events in the \etau channel are selected using a trigger which requires an electron at \ac{L1}, and both an electron
and a hadronic tau in the \ac{HLT}.
The hadronic
tau is reconstructed in a similar way as for the trigger in the \mutau channel, and loose ID and isolation requirements
are also applied to the electron at this stage.

After the trigger selection, an oppositely charged \etau pair is required, again separated by $\Delta R >0.5$. 
The electron should have a \pT~of at least $24\,\GeV$, $|\eta| < 2.1$, and should
satisfy $d_{xy} < 0.045\,\cm$ and $d_{z} < 0.2\,\cm$. The electron must pass the tight
working point of the electron MVA ID discriminator, and the
relative isolation is required to be $I_{\text{rel}}^{\Pe} < 0.1$. The requirements placed on the
hadronic tau are similar to those required in the \mutau channel, apart from the anti-$\Pgm$ discriminator,
where the loose working point is required, and the anti-$\Pe$ discriminator, where the medium
working point of the MVA discriminator is required.

If there is more than one possible \etau pair, the pair with the largest \pT$^{\Pe}$+\pT$^{\Pgth}$
is taken. Similar additional vetoes as in the \mutau channel are applied.
The event is rejected if an opposite-charge pair of electrons with \pT~ $> 15\,\GeV$, passing looser ID and
isolation requirements than the signal electron requirements, can be formed. To prevent overlap with other channels and to reduce the di-boson
background, events that have more than one electron or at least one muon passing \pT~$>10\,\GeV$ and loose ID and isolation
requirements are rejected.

In addition to the requirements on the di-tau pair, at least two jets with \pT~$>20\,\GeV$ are 
required.

@@

\subsection{Categorisation}
\label{sec:hhh_selection_categories}
In both channels a selection on the transverse mass, \mT, between the electron or muon
and missing transverse energy, defined as,
\begin{equation}\label{eqn:hhh_selection_mt}
m_{\text{T}} = \sqrt{2p_{\text{T}}E_{\text{T}}^{\text{miss}}(1-\cos{\Delta\phi})}\,,
\end{equation}
is applied.
In this eqation \pT~is the transverse momentum of the electron or muon, and $\Delta\phi$ the azimuthal
angle between this light lepton and the missing transverse energy. The \mT~distributions for the \etau
and \mutau channels, using the selections as
described in sections \ref{sec:hhh_selection_mutau} and \ref{sec:hhh_selection_etau},
are shown in figure \ref{fig:Hhh_selection_mt}.

\begin{figure}[h!]
\begin{center}
\subfloat[\mutau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mt_1_2jetinclusive_mt_2012.pdf}}
\subfloat[\etau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mt_1_2jetinclusive_et_2012.pdf}}
\end{center}
\caption[\mT~distributions in the \mutau and \etau channels.]{\mT~distributions in the (a) \mutau and (b) \etau channels.}
\label{fig:Hhh_selection_mt}
\end{figure}

This quantity is required to be smaller than $30\,\GeV$ in both channels. In events
where the missing energy and the light lepton are oriented back-to-back, \mT~is
large, whereas it is closer to zero when the two are aligned. In $\PW\rightarrow\ell\nu$
events, as the \PW boson is very heavy, the lepton and neutrino are more likely to be emitted back-to-back,
therefore \mT~will be large. For \Ztautau and \htotautau events, the neutrinos in the $\tau\rightarrow\ell\nu\nu$ decay 
 are more likely to travel in the same direction as the visible decay products of 
the tau, due to the smaller mass of the \Pgt compared with the \PW boson. Therefore requiring the
transverse mass to be less than $30\,\GeV$ reduces the \Wjets background. This effect
is also visible in figure \ref{fig:Hhh_selection_mt}, where the \Wjets and the much
smaller di-boson and single-top backgrounds are combined into the ``electroweak'' background contribution, drawn in red.
%In this analysis the presence of at least 2 jets increases the relative fraction of \ttbar 
%background events. Because the missing energy can now originate from multiple
%heavy objects (two tops) the missing transverse energy alignment is randomised. In some
%cases the lepton and missing transverse energy can be very much like the W decay
%topology, whereas in other cases \mT will be lower

After applying the \mT~selection, events are divided into three categories to maximise
sensitivity to the signal: 2jet-0tag (at least two jets, none of which are b-tagged), 2jet-1tag 
(at least two jets, exactly one of which is b-tagged), 2jet-2tag (at least two jets, at least two of which are b-tagged).
Jets are considered b-tagged if they pass the medium working point of the \ac{CSV} b-tagging discriminator.
The 2jet-0tag category does not collect much of the signal and is dominated by 
backgrounds, the 2jet-2tag category is the most sensitive to signal. 
Figure \ref{fig:Hhh_selection_bjets}, which shows the number of b-tagged jets in the two-jet selection of the \mutau and \etau
channels, illustrates this.

\begin{figure}[h!]
\begin{center}
\subfloat[\mutau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/n_bjets_csv_2jetinclusive_mt_2012_log.pdf}}
\subfloat[\etau channel]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/n_bjets_csv_2jetinclusive_et_2012_log.pdf}}
\end{center}
\caption[Number of b-tagged jets in the two-jet selection of the \mutau and \etau channels.]{Number of b-tagged jets in the two-jet selection of the (a) \mutau and (b) \etau channels. The signal
at \mH~$=300\,\GeV$ and \tanb~$=2$ in the \ac{MSSM} low-\tanb~scenario, multiplied by a factor of 10, is overlaid.}
\label{fig:Hhh_selection_bjets}
\end{figure}

In signal events the di-tau pair and di-jet pair 
are the decay products of a $125\,\GeV$ Higgs boson, therefore their invariant
masses should be close to $125\,\GeV$. To reduce background contributions
from events where the di-tau or di-jet mass is not compatible with
$125\,\GeV$, requirements are made on the di-jet invariant mass, and the di-tau
invariant mass as reconstructed using the \texttt{SVFit} algorithm \cite{HDiscoveryCMS,SVFit}. This algorithm provides
a likelihood-based estimate of the di-tau mass using the visible decay products
of the taus and the reconstructed \MET. The use of this algorithm greatly
improves the separation between $\PZ\rightarrow\Pgt\Pgt$ and $\PHiggs\rightarrow\Pgt\Pgt$ events, 
which is of great importance for the \ac{SM} $\PHiggs\rightarrow\Pgt\Pgt$ analysis \cite{HDiscoveryCMS}.
By requiring $70 < m_{jj} < 150\,\GeV$ and $90 < m_{\Pgt\Pgt} < 150\,\GeV$ a 
large number of background events can be rejected, while retaining
most of the signal. This is illustrated in figure \ref{fig:Hhh_selection_masscuts} for 
the 2jet-2tag category.

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\Pgt\Pgt}$]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/m_sv_2jet2tag_mt_2012.pdf}}
\subfloat[$m_{jj}$ ]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/mjj_2jet2tag_mt_2012.pdf}}
\end{center}
\caption[Reconstruced di-tau invariant mass and di-jet invariant mass in
the 2jet-2tag category of the \mutau channel.]{(a) Reconstructed di-tau invariant mass and (b) di-jet invariant mass in the 2jet-2tag category of the \mutau
channel. The signal for a heavy Higgs boson \PHiggs with mass \mH~$= 300\,\GeV$ at \tanb~$=2$ in the low-\tanb~MSSM scenario, multiplied by a factor 10, is overlaid.
The signal peaks at around $125\,\GeV$ in both variables.}
\label{fig:Hhh_selection_masscuts}
\end{figure}

\section{\acl{MC} simulation to data correction factors}
\label{sec:hhh_datamc}
\ac{MC} samples are used for the estimation of some of the backgrounds and the signal, 
and it is therefore important to correct for any mis-modelling. The \ac{MC} simulation to data 
correction factors used for this are estimated in dedicated control regions.

Identification, isolation, and trigger efficiencies are measured for electrons, muons
and hadronic taus in data and simulated events.
The difference between
the efficiencies in data and simulated events are applied to \ac{MC} events as a
scale factor $\text{SF} = \frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.

For electrons and muons these efficiencies are measured using a 
tag-and-probe method using \Zeenog and \Zmmnog events, respectively.
The hadronic tau identification, isolation and trigger efficiencies
are measured via a similar method that makes use of
$\PZ\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgth$ events.

The energy scale for hadronic taus is determined by fitting the mass of the 
hadronic tau candidate in $\PZ\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgth$ events.
This fit is performed separately for each hadronic tau decay mode to obtain
an energy scaling that is applied to reconstructed hadronic taus matched
to simulated hadronic tau decays in \ac{MC} events.

In the \etau channel a scale factor is applied
to the \Zee background to correct for differences in the $\Pe\rightarrow\Pgth$
fake rate between data and simulation. This scale factor is derived separately
for the 1-prong + 0$\pi^0$ and 1-prong + at least one
$\pi^0$ decay modes by fitting the visible mass of the \etau pair
in events passing the selection of the \etau channel as described in section
\ref{sec:hhh_selection_etau}, but with the two-jet requirement removed.

Differences in \MET~resolution and response between data and simulation are accounted for by
applying recoil corrections to \Zellell, \Wjets and signal \ac{MC} events. Section \ref{sec:objects_met_recoilcorr} 
gives more details on how these corrections are derived.

To correct for the differences in b-tagging efficiency and light jet mis-tagging
rates between data and simulation, \pT~and $\eta$~dependent scale factors are 
derived using the method described in reference \cite{BTV8TeV}. There are separate scale factors for 
b-/c-jets and light jets. In this analysis the ``promote/demote'' method
is used to apply these.

In this method a demotion or promotion probability is assigned to every
jet as:
\begin{align}\label{eqn:promotedemote}
&P(\text{demote}) = 1 - \text{SF} \text{  for SF < 1 }  \notag \\
&P(\text{promote}) = \frac{(\text{SF} - 1)(\epsilon_{\text{MC}}-1)}{\text{SF}} \text{    for SF > 1},
\end{align}
Where SF is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
the b-tagging efficiency in \ac{MC} events for the type of jet (light, b- or c-)
under consideration.

\section{Discriminating variable}
\label{sec:hhh_discr}
The variable of interest in this analysis is the mass of the heavy Higgs boson \PHiggs. This can be
reconstructed as the four-body mass of the two jets and the two taus. 
A more accurate result can be obtained by using a kinematic fitting 
procedure that makes use of the $125\,\GeV$ mass constraint on the di-tau and
di-jet candidates.
